Value-Suppressing Uncertainty Maps

### 2017-12-22 paper/main.tex
EOD 2/22

However, for bivariate color maps, where often the color properties used to encode value and uncertainty are not perceptually separable, error in decoding values can be quite high.  In our identification experiment, this perceptual error was high. Continuous maps performed the worst of all of our other bivariate map types (47\% vs. 63\% accuracy for discrete maps). This is likely due to the non-linearity of

@@

We designed VSUPs to promote risk-averse decision-making. In the limit of uncertainty VSUPs have only one output color, and so explicitly prevent any decoding of value. This narrowing of options is reflected not only in the quantization scheme, but also in the shape of the legend, narrowing as the uncertainty increases. This is despite the fact that the continuous maps were constructed via interpolations in CIELAB colorspace, which was designed for perceptual uniformity~\cite{mahy1994evaluation}. 
%\sizeFig

>>>>

However, for bivariate color maps, where often the color properties used to encode value and uncertainty are not perceptually separable, error in decoding values can be quite high.  In our identification experiment, this perceptual error was high. Continuous maps performed the worst of all of our other bivariate map types (47\% accuracy vs. 63\% accuracy for discrete maps). We believe that the main driver for this poor performance

@@

We designed VSUPs to promote risk-averse decision-making. In the limit of uncertainty VSUPs have only one output color, and so explicitly prevent any decoding of value. This narrowing of options is reflected not only in the quantization scheme, but also in the shape of the legend, narrowing as the uncertainty increases. This is despite the fact that the continuous maps were constructed via interpolations in CIELAB colorspace, which was designed for perceptual uniformity~\cite{mahy1994evaluation}. The integrality of the value and uncertainty channels 
%\sizeFig
